LogChunks: A Data Set for Build Log Analysis

### 2020-03-10 msr-paper/paper.tex
few more edits, smaller listing textsize

We believe that having a common data set to compare
different build log analysis techniques fairly will advance the research
area. It will ultimately increase our understanding of CI build
failures. In this paper, we present \logchunks, a collection of 797
annotated Travis CI build logs from 80 GitHub repositories in 29
programming languages. For each build log, \logchunks contains a
manually labeled log part (chunk) describing why the build failed. We
externally validated the data set with the developers who caused the
original build failure.

@@

\paragraph{Build Sampling}
To sample the builds for \logchunks we keep the most recent ten of the status 
\emph{failed}~\cite{travis2009buildstatus}. We check up to 1,000 builds per 
repository to ensure predictable termination of the log collection.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

@@

\lstset{
  language=XML,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[tbp]
	\centering
\begin{lstlisting}[breaklines=true]
========DIFF========
*{\color{cyan}-=-=-=-=-=-}*
005+     Parameter #1 [<optional> $flags]
005-     Parameter #1 [<optional> $ar_flags]
========DONE========
FAIL Bug#71412 ArrayIterator reflection 
*{\color{cyan}-=-=-=-=-=-}*
TEST 9895/13942 [2/2 test workers running]
\end{lstlisting}
\vspace{-0.3cm}
	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}. We inserted the special marker ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
	\label{lst:same-category}
\end{figure}

>>>>

We believe that having a common data set to compare
different build log analysis techniques will advance the research
area. It will ultimately increase our understanding of CI build
failures. In this paper, we present \logchunks, a collection of 797
annotated Travis CI build logs from 80 GitHub repositories in 29
programming languages. For each build log, \logchunks contains a
manually labeled log part (chunk) describing why the build failed. We
externally validated the data set with the developers who caused the
original build failure.

@@

\paragraph{Build Sampling}
To sample builds for \logchunks we keep the ten most recent builds of the status 
\emph{failed}~\cite{travis2009buildstatus}. We check up to 1,000 builds per 
repository to ensure predictable termination of the log collection.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

@@

\lstset{
  language=XML,
  basicstyle=\footnotesize,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[tbp]
	\centering
\begin{lstlisting}[breaklines=true]
========DIFF========
*{\color{cyan}-=-=-=-=-=-}*
005+     Parameter #1 [<optional> $flags]
005-     Parameter #1 [<optional> $ar_flags]
========DONE========
FAIL Bug#71412 ArrayIterator reflection 
*{\color{cyan}-=-=-=-=-=-}*
TEST 9895/13942 [2/2 test workers running]
\end{lstlisting}
\vspace{-0.3cm}
	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}. We inserted the special marker ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
	\label{lst:same-category}
\end{figure}
